\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemSingle}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Benjamin Don} & Email : \href{mailto:bddon466@gmail.com}{bddon466@gmail.com}\\
  \href{https://benjidon.github.io}{https://benjidon.github.io} & Mobile : +1-949-528-5631 \\
\end{tabular*}

%-----------SUMMARY-----------------
\begin{flushleft}
\small{
Senior Full-Stack Engineer at Intuit with 5+ years building production applications and distributed systems. Deep expertise in React, TypeScript, and Kotlin/Spring Boot, delivering end-to-end features from user interface to scalable backend infrastructure.
}
\end{flushleft}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intuit}{Mountain View, CA}
      {Senior Software Engineer - Search}{Feb. 2025 - Present}
      \resumeItemListStart
        \resumeItemSingle{Built GraphQL-based Search Service using Kotlin and Spring Boot, unifying data access across QuickBooks microservices as the primary search backend serving 20M+ daily requests}
        \resumeItemSingle{Engineered reactive service using Kotlin coroutines and optimized thread pools, reducing infrastructure costs by improving concurrent request handling with lower CPU/memory footprint}
        \resumeItemSingle{Designed object-oriented search provider framework, accelerating feature velocity and enabling rapid integration of new search clients}
        \resumeItemSingle{Architected intelligent cache invalidation system for search results using Valkey/ElastiCache, achieving 80\% latency reduction, 40\% hit rate, and reduced infrastructure costs}
        \resumeItemSingle{Developed AI-powered semantic search using vector embeddings, enabling natural language query processing and complex search operations}
        \resumeItemSingle{Created performance testing framework using WireMock to simulate faults and progressive load in pre-production, preventing incidents and enabling confident scaling}
        \resumeItemSingle{Established CI/CD pipeline for weekly releases with comprehensive instrumentation and on-call alerting infrastructure}
        \resumeItemSingle{Contributed to MCP-based agent for Claude that auto-generates Wavefront dashboards from application metrics, enabling engineers to bootstrap observability in minutes instead of hours}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer II - Search}{Feb. 2023 - Jan. 2025}
      \resumeItemListStart
        \resumeItemSingle{Modernized QuickBooks search bar UI using React Hooks and responsive design, increasing search adoption by 30\% through improved user experience}
        \resumeItemSingle{Designed and implemented full-stack self-service portal (React + Java REST API) during hackathon, enabling PMs to manage search routes and eliminating manual engineer uploads}
        \resumeItemSingle{Architected AWS S3 data pipeline to migrate static search routes from legacy service to modern search backend}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer - Audit Log}{Sep. 2021 - Jan. 2023}
      \resumeItemListStart
        \resumeItemSingle{Led Transaction History redesign as part of monolith-to-microservices migration, building React components for new backend architecture}
        \resumeItemSingle{Built high-demand CSV export feature using parallel API requests and client-side aggregation, serving 10K+ daily users}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer Intern}{Jun. 2020 - Sep. 2020}
      \resumeItemListStart
        \resumeItemSingle{Delivered mobile-first responsive UI improvements for QuickBooks web app}
      \resumeItemListEnd

    \resumeSubheading
      {Tapestry Solutions}{San Luis Obispo, CA}
      {Software Developer}{Jul. 2018 - Dec. 2019}
      \resumeItemListStart
        \resumeItemSingle{Built React-based inventory management system for military supply chain operations}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages:} JavaScript/TypeScript, Kotlin, Java, Python, SQL \\
     \textbf{Frontend:} React, React Hooks, Responsive Design, Modern CSS \\
     \textbf{Backend:} Spring Boot, Node.js, GraphQL, Elasticsearch, Redis, Microservices \\
     \textbf{Cloud \& DevOps:} AWS (S3, EC2, Lambda), Kubernetes, Docker, CI/CD Pipelines
    }}
 \end{itemize}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {California State Polytechnic University}{San Luis Obispo, CA}
    {Bachelor of Science in Computer Science}{Mar. 2021}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
