\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemSingle}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Benjamin Don}} & Email : \href{mailto:bddon466@gmail.com}{bddon466@gmail.com}\\
  \href{https://benjidon.github.io}{https://benjidon.github.io} & Mobile : +1-949-528-5631 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intuit}{Mountain View, CA}
      {Senior Software Engineer - Search}{Dec. 2024 - Present}
      \resumeItemListStart
        \resumeItemSingle{Built GraphQL-based Search Service using Kotlin and Spring Boot, unifying data access across QuickBooks microservices as the primary search backend serving 20M+ daily requests}
        \resumeItemSingle{Engineered reactive service using Kotlin coroutines and optimized thread pools, reducing infrastructure costs by improving concurrent request handling with lower CPU/memory footprint}
        \resumeItemSingle{Designed object-oriented search provider framework, accelerating feature velocity and enabling rapid integration of new search clients}
        \resumeItemSingle{Architected intelligent cache invalidation system for search results using Valkey/ElastiCache, achieving 80\% latency reduction and 40\% hit rate while maintaining data consistency across dynamic entity updates}
        \resumeItemSingle{Developed AI-powered semantic search using vector embeddings, enabling natural language query processing and complex search operations}
        \resumeItemSingle{Created performance testing framework using WireMock to simulate faults and progressive load in pre-production, preventing incidents and enabling confident scaling}
        \resumeItemSingle{Established CI/CD pipeline for weekly releases with comprehensive instrumentation and on-call alerting infrastructure}
        \resumeItemSingle{Contributed to MCP-based agent for Claude that auto-generates Wavefront dashboards from application metrics, enabling engineers to bootstrap observability in minutes instead of hours}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer II - Search}{Jan. 2023 - Nov. 2024}
      \resumeItemListStart
        \resumeItemSingle{Modernized QuickBooks search bar UI using React Hooks and responsive design, increasing search adoption by 30\% through improved user experience}
        \resumeItemSingle{Designed and implemented full-stack self-service portal (React + Java REST API) during hackathon, enabling PMs to manage search routes and eliminating manual engineer uploads}
        \resumeItemSingle{Architected AWS S3 data pipeline to migrate static search routes from legacy service to modern search backend}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer - Audit Log}{Sep. 2021 - Dec. 2022}
      \resumeItemListStart
        \resumeItemSingle{Led Transaction History redesign as part of monolith-to-microservices migration, building React components for new backend architecture}
        \resumeItemSingle{Built high-demand CSV export feature using parallel API requests and client-side aggregation, serving 10K+ daily users}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer Intern}{Jun. 2020 - Sep. 2020}
      \resumeItemListStart
        \resumeItemSingle{Delivered mobile-first responsive UI improvements for QuickBooks web app}
      \resumeItemListEnd

    \resumeSubheading
      {Tapestry Solutions}{San Luis Obispo, CA}
      {Software Developer}{Jul. 2018 - Dec. 2019}
      \resumeItemListStart
        \resumeItemSingle{Built React-based inventory management system for military supply chain operations}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages:} Kotlin, Java, JavaScript/TypeScript, Python, SQL \\
     \textbf{Frameworks \& Tools:} Spring Boot, React, Node.js, GraphQL, Elasticsearch, Redis, Docker \\
     \textbf{Cloud \& DevOps:} AWS (S3, EC2, Lambda), Kubernetes, CI/CD Pipelines, Microservices Architecture
    }}
 \end{itemize}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {California State Polytechnic University}{San Luis Obispo, CA}
    {Bachelor of Science in Computer Science}{Sep. 2016 -- Mar. 2021}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

% %-----------PROJECTS (COMMENTED OUT)-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
% 
%    \resumeSubheading
%       {Ray Tracer}{}
%       {Written in C++.}{Sep. 2020 - Dec. 2020}
%       \resumeItemListStart
%         \resumeItemSingle {Implemented custom vector / math classes to support ray collisions.}
%         \resumeItemSingle {Supports OBJ files and multiple materials, from diffuse to refractive surfaces.}
%         \resumeItemSingle {Includes support for volume rendering through voxel data.}
%       \resumeItemListEnd
% 
%          \resumeSubheading
%       {Lightspeed Breakout}{}
%       {Written in C++}{Apr. 2020 - Jun. 2020}
%       \resumeItemListStart
%         \resumeItemSingle {Created a stage sci-fi escape game, you play as an imprisoned passenger aboard a perilous space station.}
%         \resumeItemSingle {Worked with a team to create a game engine from scratch for the project.}
%         \resumeItemSingle {Gained experience with OpenGL, GLM, and GLSL for rendering, and irrKlang for audio.}
%         \resumeItemSingle {Implemented a quaternion based rotation scheme.}
%         \resumeItemSingle {Developed a 2D render system to support dynamic HUD elements.}
%       \resumeItemListEnd
% 
%   %  \resumeSubheading
%   %     {Camp Redpines}{}
%   %     {Unity, Written in C Sharp}{Sep. 2020 - Mar. 2021}
%   %     \resumeItemListStart
%   %       \resumeItemSingle {Created a short game set in a campground with multiple activities, meant to relax the player.}
%   %       \resumeItemSingle {Developed with Unity's Universal Rendering Pipeline.}
%   %       \resumeItemSingle {Built custom shaders with Unity's shader graph interface.}
%   %       \resumeItemSingle {Worked with Blender to rig and animate 3D models.}
% 
%       % \resumeItemListEnd
% 
%   \resumeSubHeadingListEnd
